---
title       : Model Evaluation on Personal Activity Data
subtitle    : Coursera Data developing Products Course
author      : Created By Deepak on Aug 15th, 2015

job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
url: 
  assets: /assets
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Synopsis
 
 
 
 
- Jawbone, Nike, Fitbit enable collection of personal activity data

- Measure how much of a particular activity is carried out

- Do we measure how well these activities are carried out?

- 'How well' provides useful information for personal health & sports training

- App at: https://bdexpert.shinyapps.io/ModelEvaluation 

--- .class #id 


## Model
 

- User selects a model to evaluate

- App outputs the model's accuracy

- Compare output of multiple models easily by selecting the desired model

- Original Dataset consists of 19622 obs and 134 variables

- Final dataset consisted of 52 predictors and 1 response

- Model evaluated on training and cross validation data

- Model Options
 - LDA
 - QDA
 - KNN
 - Classification Trees

--- .class #id 




## Dendogram for Classification Trees

```{r echo=FALSE, results='hide'}
library(caret)
library(rpart.plot)
library(rpart)
library(curl)
library(ggplot2)
library(lattice)
```

```{r echo=FALSE}
## Input Data
training_url = "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
training_file = "pml-training.csv"
if (!file.exists(training_file)){download.file(url=training_url, destfile=training_file, method="curl")}

testing_url = "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
testing_file = "pml-testing.csv"
if (!file.exists(testing_file)) {download.file(url=testing_url, destfile=testing_file, method="curl")}

# Import the data and convert blanks and DIV errors as NA.
train = read.csv("pml-training.csv", na.strings=c('NA','','#DIV/0!'), header=TRUE)
train_cols = colnames(train)
test = read.csv("pml-testing.csv", na.strings=c('NA','','#DIV/0!'), header=TRUE)
test_cols = colnames(test)

# Verify that the column names (excluding classe and problem_id) are identical in the training and test set.
#all.equal(train_cols[1:length(train_cols)-1], test_cols[1:length(test_cols)-1])


#Remove NA columns from training and test dataset

NAindex = apply(train,2,function(x) {sum(is.na(x))}) 
trainNA = train[,which(NAindex == 0)]
testNA = test[,which(NAindex == 0)]

train_cols = colnames(trainNA)
test_cols = colnames(testNA)
#all.equal(train_cols[1:length(train_cols)-1], test_cols[1:length(test_cols)-1])

#Remove unnecessary columns like timestamps, usernames, etc
trainNA = trainNA[,8:length(names(trainNA))]
testNA = testNA[,8:length(names(testNA))]

#center and scale the variables
preproc = preProcess(trainNA[,-53],method=c('center', 'scale'))
trainproc = predict(preproc, trainNA[,-53])
trainproc$classe = trainNA$classe

testproc = predict(preproc,testNA[,-53])

#Create a validation set out of the training set in a 60%-40% ratio.
set.seed(12031987)

inTrain = createDataPartition(trainproc$classe, p = 0.6, list=FALSE)
training = trainproc[inTrain,]
crossValidation = trainproc[-inTrain,]

modFittree <- train(classe ~ ., data = training, method="rpart")
predtree = predict(modFittree, newdata=crossValidation)

rpart.plot(modFittree$finalModel)
```


--- .class #id 

## Confusion Matrix Output for Classification Trees


```{r echo=FALSE}
print(confusionMatrix(predtree, crossValidation$classe), digits=4)
```
